Formalizing the Kolmogorov extension Theorem in Lean

### 2023-09-14 Manuscript/proof_outline.tex
change countably to sigma in lemma names

Note that the assumption \leanline{hP_inner} from above translates
directly to inner regularity of the \leanlinecolor{kolContent}, which
is defined through the projective family \leanline{P}. Moreover, since
the Carathéodory extension theorem requires $\sigma$-subadditivity
(rather than $\sigma$-additivity), we can use
\leanlinecolor{countably_subadditive_of_countably_additive} in order
to show
\leanlinecolor{kolContent_countably_subadditive_of_innerRegular}, and
the assumptions of the last result also imply $\sigma$-subadditivity.

%  theorem kolContent_countably_subadditive_of_innerRegular
%    (hP : IsProjectiveMeasureFamily P)
%    (hP_inner : ∀ J,
%      (P J).InnerRegular (fun s => IsCompact s ∧ IsClosed s)
%      MeasurableSet)
%    ⦃f : ℕ → Set (∀ i, α i)⦄
%    (hf : ∀ i, f i ∈ cylinders α)
%    (hf_Union : (⋃ i, f i) ∈ cylinders α) :
%    kolContent hP (⋃ i, f i) ≤ ∑' i, kolContent hP (f i)

@@

\begin{minted}[highlightlines={1}, mathescape, numbersep=5pt, framesep=5mm, bgcolor=mygray]{Lean}
def projectiveLimitWithWeakestHypotheses
    (P : ∀ J : Finset ι, Measure (∀ j : J, α j))
    (hP : IsProjectiveMeasureFamily P) :
    Measure (∀ i, α i) :=
  Measure.ofAddContent setSemiringCylinders
    generateFrom_cylinders (kolContent hP)
    (kolContent_countably_subadditive_of_innerRegular hP
      fun J => innerRegular_isCompact_isClosed_
      measurableSet_of_complete_countable (P J))    
\end{minted}
\sloppy Let us look closer at the formalized proof:
\leanlinecolor{kolContent_countably_subadditive_of_innerRegular} has
the same hypotheses as
\leanlinecolor{kolContent_sigma_additive_of_innerRegular}, except
\leanline{h_disj}. So, the lemma in the last brackets shows
$\sigma$-sub-additivity of the content $P$ from
Theorem~\ref{T1}. Then, \leanlinecolor{generateFrom_cylinders} gives
the \leanline{MeasurableSpace} on which we define the
\leanlinecolor{addContent}.

>>>>

Note that the assumption \leanline{hP_inner} from above translates
directly to inner regularity of the \leanlinecolor{kolContent}, which
is defined through the projective family \leanline{P}. Moreover, since
the Carathéodory extension theorem requires $\sigma$-subadditivity
(rather than $\sigma$-additivity), we can use
\leanlinecolor{sigma_subadditive_of_sigma_additive} in order
to show
\leanlinecolor{kolContent_sigma_subadditive_of_innerRegular}, and
the assumptions of the last result also imply $\sigma$-subadditivity.

%  theorem kolContent_sigma_subadditive_of_innerRegular
%    (hP : IsProjectiveMeasureFamily P)
%    (hP_inner : ∀ J,
%      (P J).InnerRegular (fun s => IsCompact s ∧ IsClosed s)
%      MeasurableSet)
%    ⦃f : ℕ → Set (∀ i, α i)⦄
%    (hf : ∀ i, f i ∈ cylinders α)
%    (hf_Union : (⋃ i, f i) ∈ cylinders α) :
%    kolContent hP (⋃ i, f i) ≤ ∑' i, kolContent hP (f i)

@@

\begin{minted}[highlightlines={1}, mathescape, numbersep=5pt, framesep=5mm, bgcolor=mygray]{Lean}
def projectiveLimitWithWeakestHypotheses
    (P : ∀ J : Finset ι, Measure (∀ j : J, α j))
    (hP : IsProjectiveMeasureFamily P) :
    Measure (∀ i, α i) :=
  Measure.ofAddContent setSemiringCylinders
    generateFrom_cylinders (kolContent hP)
    (kolContent_sigma_subadditive_of_innerRegular hP
      fun J => innerRegular_isCompact_isClosed_
      measurableSet_of_complete_countable (P J))    
\end{minted}
\sloppy Let us look closer at the formalized proof:
\leanlinecolor{kolContent_sigma_subadditive_of_innerRegular} has
the same hypotheses as
\leanlinecolor{kolContent_sigma_additive_of_innerRegular}, except
\leanline{h_disj}. So, the lemma in the last brackets shows
$\sigma$-sub-additivity of the content $P$ from
Theorem~\ref{T1}. Then, \leanlinecolor{generateFrom_cylinders} gives
the \leanline{MeasurableSpace} on which we define the
\leanlinecolor{addContent}.
